---
title: "Homework 1: ggplot2"
author: "Denys Bondar"
date: "2019-03-05"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

By using *mpg* dataset:
```{r}
mpg
```
1. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

- Color
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = manufacturer, color= (displ)))
```
- Size
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = manufacturer, size = (displ)))
```

- Shape
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = manufacturer, shape = (displ)))
```

4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = manufacturer, size = (displ), color = displ< 5))
```
2. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = manufacturer, size = (displ), color = (displ)))
```
```

3. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
It changes border size of points. That is why it can change only shapes with
```

4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}
It turns displ < 5 into a boolean (or dummy) variable on the fly and maps that T or F to the colour argument.
```